Interfacing logic programming and Coq

### 2020-10-30 papers/types2020/elab.tex
Minor rewording

\item Check proofs by executing the logic programming checker that is
  parametrized by the particular FPC definition.
\end{enumerate}
%
It is also possible to pair two different proof certificates,
following two different FPC definitions and to do the proof checking
in parallel.  The logic programming setting allows such parallel
checking to also be checking-and-synthesizing.  That is, during the
checking of one certificate, it is possible to synthesize, for
example, a fully detailed term that is appropriate for handing to the
Coq kernel.

>>>>

\item Check proofs by executing the logic programming checker that is
  parametrized by the particular FPC definition.
\end{enumerate}
%
It is also possible to pair two different proof certificates, defined
by two different FPC definitions, and do the proof checking in
parallel.  The logic programming setting allows such parallel checking
to also serve as checking-and-synthesizing.  That is, during the
checking of one certificate, it is possible to synthesize, for
example, a fully detailed term that is appropriate for handing to the
Coq kernel.
